Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-06-17 paper/results.tex
minor adjustments

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{exp1_slice0}
	\includegraphics[width=0.9\linewidth]{exp1_slice1}
	\includegraphics[width=0.9\linewidth]{exp1_slice2}
	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) with 3~selected discrete feature assignments.}
\end{figure}

@@

\begin{table*}
	\centering
	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
		average values and standard deviations are reported over 5~cross-validation folds,
		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
		and $\omega$ is a relative speedup with respect to
		$\overline{t}_{\text{eval.}}=\num{7.777049573054314} \pm
		\num{2.8103592103930337} \text{ s}$
		measured in the MC TBR model over~\num{500000} samples.
	The best-performing method(s) under each are highlighted in bold.}
	\setlength\tabcolsep{4pt}
	\begin{indented}
	\item[]
		\scriptsize
		\begin{tabular}{lrrrrrrrr}
		\toprule
		{} & {} & \multicolumn{4}{c}{Regression performance} &
		\multicolumn{3}{c}{Computational complexity}\\
		\cmidrule(lr){3-6}
		\cmidrule(lr){7-9}
		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
		\midrule
		\input{tbl/table11}
		\bottomrule
		\end{tabular}
	\end{indented}
\end{table*}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{exp1_slice0}
	\includegraphics[width=0.9\linewidth]{exp1_slice1}
	\includegraphics[width=0.9\linewidth]{exp1_slice2}
	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
		terms of complexity (as~$\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) with 3~selected discrete feature assignments.}
\end{figure}

@@

\begin{table*}
	\centering
	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
		average values and standard deviations are reported over 5~cross-validation folds,
		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
		and $\omega$ is a relative speedup with respect to
		$\overline{t}_{\text{eval.}}=\num{7.777049573054314} \pm
		\num{2.8103592103930337} \text{ s}$
		measured in the MC TBR model over~\num{500000} samples.
	The best-performing method(s) under each are highlighted in bold.}
	\setlength\tabcolsep{4pt}
	\begin{indented}
	\item[]
		\scriptsize
		\begin{tabular}{lrrrrrrrr}
		\toprule
		{} & {} & \multicolumn{4}{c}{Regression performance} &
		\multicolumn{3}{c}{Complexity}\\
		\cmidrule(lr){3-6}
		\cmidrule(lr){7-9}
		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
		\midrule
		\input{tbl/table11}
		\bottomrule
		\end{tabular}
	\end{indented}
\end{table*}
